Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
in recap tab too

\begin{table}[H]
\centering
\caption{Comparison (ROC) with other methods (for now, $t = 0.11$)}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation (best)         & 0.886 & 0.884 & 0.891 & 0.877\\
Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\
Our approach               & & & & \\
GENIE3                     & & & & \\
GTE                        & & & & \\
Directivity                & 0.535 & 0.526 & 0.533 & 0.535 \\
Our approach + dir         & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Comparison (P-R) with other methods (for now, $t = 0.11$)}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation (best)         & 0.153 & 0.145 & 0.170 & 0.132 \\
Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (best)        & & & & \\
GENIE3                     & & & & \\
GTE                        & & & & \\
Directivity                & 0.012 & 0.012 & 0.012 & 0.012\\
Our approach + dir         & & & & \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\centering
\caption{Comparison (ROC) with other methods (for now, $t = 0.11$)}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation (best)         & 0.886 & 0.884 & 0.891 & 0.877\\
Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\
Our approach               & 0.943 & 0.942 & 0.942 & 0.939 \\
GENIE3                     & & & & \\
GTE                        & & & & \\
Directivity                & 0.535 & 0.526 & 0.533 & 0.535 \\
Our approach + dir         & 0.944 & 0.943 & 0.942 & 0.940\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Comparison (P-R) with other methods (for now, $t = 0.11$)}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation (best)         & 0.153 & 0.145 & 0.170 & 0.132 \\
Partial correlation (best) & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (best)        & 0.403 & 0.404 & 0.398 & 0.388 \\
GENIE3                     & & & & \\
GTE                        & & & & \\
Directivity                & 0.012 & 0.012 & 0.012 & 0.012 \\
Our approach + dir         & 0.404 & 0.405 & 0.399 & 0.389 \\
\bottomrule
\end{tabular}
\end{table}
